---
title: "MILLS_Skills_Test_3"
author: "Cameron Mills"
date: "11/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(modelr)
library(janitor)
library(broom)

```

Loading in data and cleaning it up: 
```{r}
df <- read_csv("C:/Users/email/Data_Course_MILLS/Exams/Exam 3/Data/FacultySalaries_1995.csv")
clean_names(df)

df <- 
df %>% 
  pivot_longer(cols = contains(c("FullProfSalary", "AssocProfSalary", "AssistProfSalary")), 
               names_to = "Rank_Salary", 
               values_to = "Salary")

df <- 
  df %>% pivot_longer(cols = contains(c("FullProfComp", "AssocProfComp", "AssistProfComp", "CompAll")), 
                      names_to = "Rank_Comp", 
                      values_to = "Comp")

df <- 
  df %>% pivot_longer(cols = contains(c("FullProfs", "AssocProfs", "AssistProfs")), 
                      names_to = "Rank_Profs", 
                      values_to = "Num_Profs")
```

Here is a box plot showing Salary as a function of Rank (Full, Assist, Assoc) based on their tier as well. The first box for each color is the I tier, the second box for each color is the IIA tier, and the third box for each color is the IIB  tier: 

```{r}
df %>% 
  ggplot(aes(x=Rank_Salary, y=Salary, z=Tier, fill=Rank_Salary)) + 
  geom_boxplot()

```

We will now build an ANOVA model. This model will test the influence of "State", "Tier", and "Rank" on Salary. 
```{r}
mod1 <- 
  aov(data = df, formula = Salary ~ State + Tier + Rank_Salary)
summary(mod1)
```

The rest of this report will focus on another data set:

```{r}
dat <- read_csv("C:/Users/email/Data_Course_MILLS/Exams/Exam 3/Data/Juniper_Oils.csv")

dat <- dat %>% 
  pivot_longer(cols = contains(c("ene", "ol", "al", "compound")), 
               names_to = "Compound", 
               values_to = "Conc")
```

Aaaand here's a graph

```{r}
dat %>% ggplot(aes(x=YearsSinceBurn, y=Conc)) + 
  geom_line(linetype=0) +
  geom_smooth() + 
  facet_wrap(~Compound, scales = "free")
```

Here's a generalized linear model to show concentrations that are affected by "Years Since Burn": 

```{r}
mod2 <- glm(data = dat, 
            formula = Conc ~ Compound * YearsSinceBurn * ChemMean * Tree_Species)
tidy(mod2) %>% 
  filter(p.value<0.05)

```




